On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-07-15 docs/mvfits_paper/mvf.tex
updating paper

\author{L. London}
\affiliation{\Cardiff}
\author{Edward Fauchon-Jones}
\affiliation{\Cardiff}

@@

Here, our goal is to very brielfy assess

@@

Let's start by applying \gmvr{} to a fiducial scalar function of the form

@@

Here it is demonstrated that \gmvr{} converges exponentially, as expected given th.

>>>>

\author{L. London}
\affiliation{\Cardiff}
\author{E. Fauchon-Jones}
\affiliation{\Cardiff}

@@

Here, our goal is to very briefly overview the functionality of the \gmvr{} algorithm as implemented in Ref. \red{[positive]}.

@@

While it is possible to investigate the output of \gmvr{} with varying hyper-parameters (such as the tolerance input to Alg. \ref{alg:gmvr}), we will focus only on a simple usage case.
Similarly, we note that \gmvr{} as implemented in Ref. \red{[positive]} involves a reverse (or negative) greedy step to counter over-modeling in cases where the aforementioned $tol$ is too low.
For relevance of presentation to physics examples in subsequent sections, we will restrict ourselves to a case where numerical noise is low, and the negative greedy step does not alter the output of Alg. \ref{alg:gmvr}).
\par Let's start by applying \gmvr{} to a fiducial scalar function of the form

@@

Here it is demonstrated that \gmvr{} in a way that is approximately exponential, owing to the underlying analytic nature of the training data.
